---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%",
    eval = TRUE
)
library(magrittr)
```

# nise

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/valid)](https://CRAN.R-project.org/package=valid)
<!-- badges: end -->

## Installation

You can install the development version of from [GitHub](https://github.com/) with:

```{r eval=FALSE}
# install.packages("remotes")
remotes::install_github("rappster/nise")
```

## What?

Helpers for NSE:

- `handle_nse_name()`: meant for values that denote column or list element names. It returns an object of class `name` "no matter what you throw at it". Currently you can throwvalues of class `name`/`symbol`, `character`, `quosure`.
- `handle_nse_names()`: "vectorized" version of `handle_nse_name()`

## Why?

I was looking for something that works well

- with the NSE mechanism implemented by `dplyr` and its tidyverse friends as well as the base R mechanism for subsetting column/list element names

- inside nested function calls

## How?

```{r}
library(nise)
```

Example data 

```{r}
data_tbl <- tibble::tribble(
    ~color,     ~a, ~b, ~c, ~d,
    "blue",      1,  2, TRUE, FALSE,
    "green",     6,  2, TRUE, FALSE,
    "purple",    3,  3, TRUE, FALSE,
    "red",       2,  3, TRUE, FALSE,
    "yellow",    5,  1, TRUE, FALSE
)

data_lst <- data_tbl %>% as.list()
```

### Functions `handle_nse_name()` and `handle_nse_names()`

They are typically called **within** other functions to handle argument values
of different types for column names in a data frame/tibble or names of a list.

The goal is to no matter how the value is supplied a `name` should be returned
as this seems to be the best "processed value" that plays nicely with the NSE
mechanism implemented in `dplyr` and friends.

#### Explicit arguments

```{r}
foo <- function(data, col) {
    col <- nise::handle_nse_name(col)
    data %>% dplyr::select(!!col)
}

data_tbl %>% foo(color)
data_tbl %>% foo("color")
data_tbl %>% foo(rlang::quo(color))

tmp <- rlang::sym("color")
col <- rlang::enquo(tmp)
data_tbl %>% foo(col)
```

Also works for lists

```{r}
foo_list <- function(data, name) {
    name <- nise::handle_nse_name(name)
    data %>% `[[`(name)
}
data_lst %>% foo_list(color)
data_lst %>% foo_list("color")
data_lst %>% foo_list(rlang::quo(color))

tmp <- rlang::sym("color")
col <- rlang::enquo(tmp)
data_lst %>% foo_list(col)
```

#### Implicit arguments using `...`

```{r}
bar <- function(data, ...) {
    cols <- nise::handle_nse_names(...)
    data %>% dplyr::select(!!!cols)
}
col_c <- rlang::sym("c")
col_d <- "d"
col_d_enquo <- rlang::enquo(col_d)

data_tbl %>% bar(b, rlang::quo(a), "color", col_d_enquo, col_c)
```

Also works for lists

```{r}
bar_list <- function(data, ...) {
    names <- nise::handle_nse_names(...) %>% as.character()
    data %>% `[`(names)
}
col_c <- rlang::sym("c")
col_d <- "d"
col_d_enquo <- rlang::enquo(col_d)

data_lst %>% bar_list(b, rlang::quo(a), "color", col_d_enquo, col_c)
```

#### Just looking at `handle_nse_name()` and `handle_nse_names()`

```{r}
rlang::sym("color") %>% handle_nse_name()
rlang::quo(color) %>% handle_nse_name()
"color" %>% handle_nse_name()

tmp <- rlang::sym("color")
col <- rlang::enquo(tmp)
handle_nse_name(col)
```

```{r}
var <- rlang::sym("color")
var %>% handle_nse_name()

var <- rlang::quo(color)
var %>% handle_nse_name()

var <- "color" 
var %>% handle_nse_name()

tmp <- rlang::sym("color")
var <- rlang::enquo(tmp)
var %>% handle_nse_name()
```
